\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2012-08-20 doc/USER_MANUAL/manual_SPECFEM3D.tex
improved the sentence about mcmodel=medium

If you run very large meshes on a relatively small number
of processors, the memory size needed on each processor might become
greater than 2 gigabytes, which is the upper limit for 32-bit addressing.
In this case, on some compilers you may need to add \texttt{``-mcmodel=medium}'' or \texttt{``-mcmodel=medium -shared-intel}''
to the compiler options of CFLAGS, FCFLAGS and LDFLAGS otherwise the compiler will display an error
message (for instance \texttt{``relocation truncated to fit: R\_X86\_64\_PC32 against .bss''} or something similar);
on an IBM machine with the \texttt{xlf} and \texttt{xlc} compilers, using \texttt{-q64} is usually sufficient.\\

@@

\caption{Schematic workflow for a SPECFEM3D simulation. The exectable \texttt{xgenerate\_databases} creates the GLL mesh points and assigns specific model parameters.}

>>>>

If you run very large meshes on a relatively small number
of processors, the memory size needed on each processor might become
greater than 2 gigabytes, which is the upper limit for 32-bit addressing.
In this case, on some compilers you may need to add \texttt{``-mcmodel=medium}'' or \texttt{``-mcmodel=medium -shared-intel}''
to the configure options of CFLAGS, FCFLAGS and LDFLAGS otherwise the compiler will display an error
message (for instance \texttt{``relocation truncated to fit: R\_X86\_64\_PC32 against .bss''} or something similar);
on an IBM machine with the \texttt{xlf} and \texttt{xlc} compilers, using \texttt{-q64} is usually sufficient.\\

@@

\caption{Schematic workflow for a SPECFEM3D simulation. The executable \texttt{xgenerate\_databases} creates the GLL mesh points and assigns specific model parameters.}
